Expression QTL hotspot dissection with mediation analysis and pleiotropy testing

### 2019-07-25 analysis/paper/paper.Rnw
fixed figures

<<setuprnw, include=TRUE>>=
library(knitr)
opts_chunk$set(
concordance=TRUE,
echo = FALSE,
fig.lp = "fig:",
warning = FALSE,
message = FALSE,
comment = NA
)
def.chunk.hook  <- knitr::knit_hooks$get("chunk")
knitr::knit_hooks$set(chunk = function(x, options) {
  x <- def.chunk.hook(x, options)
  ifelse(options$size != "normalsize", paste0("\\", options$size,"\n\n", x, "\n\n \\normalsize"), x)
})
options(tinytex.verbose = TRUE)
@

@@

<<count_med>>=
n_med_tr <- 4 # arbitrary threshold
n_med_per_local <- med_tib %>%
  group_by(local_symbol) %>%
  filter(lod_diff > 1.5) %>%
  count() %>%
  filter(n >= n_med_tr)

@@

<<heat9-2>>=
ord <- match(rn, rownames(pm))

pm[ord, ord] %>%
  apply(FUN = trunc2, MARGIN = 2, threshold = 5) %>%
  heatmaply(Rowv = FALSE,
            Colv = FALSE,
            cexRow = 0.2,
            cexCol = 0.2,
            symm = TRUE,
            row_side_colors = scols[ord, ],
            col_side_colors = scols1[ord],
            limits = c(0, 5)
            )
@

@@

<<ref.label = "scatter_by_local-2">>=
@

@@

<<ref.label = "make_scols-extra-2">>=
@

<<ref.label = "count_med">>=
@

<<ref.label = "heat9-2">>=
@

<<ref.label = "index-v-peak-position-2">>=
@

@@

<<ref.label = "more_setup-2">>=
@

<<ref.label="readRDS-2">>=
@

<<ref.label="make_local_annot-2">>=
@

<<ref.label = "make_nonlocal_annot-2">>=
@

<<ref.label = "make_local_annot2-2">>=
@

<<ref.label = "subset_expr_matrix-2">>=
@

<<ref.label = "tabulate-2", message=FALSE, warning = FALSE>>=
@

<<ref.label="make_pleio_tib-2">>=
@

<<ref.label = "make_pm-2">>=
@

@@

<<ref.label = "scatter_by_local-2">>=
@

<<ref.label="make_scols-2">>=
@

<<ref.label="heat8-2">>=
@

<<ref.label = "make_scols-extra-2">>=
@

<<ref.label = "count_med">>=
@

<<ref.label = "heat9-2">>=
@

<<ref.label = "index-v-peak-position-2">>=
@

@@

<<ref.label = "more_setup-2">>=
@

<<ref.label="readRDS-2">>=
@

<<ref.label="make_local_annot-2">>=
@

<<ref.label = "make_nonlocal_annot-2">>=
@

<<ref.label = "make_local_annot2-2">>=
@

<<ref.label = "subset_expr_matrix-2">>=
@

<<ref.label = "tabulate-2", message=FALSE, warning = FALSE>>=
@

<<ref.label="make_pleio_tib-2">>=
@

<<ref.label = "make_pm-2">>=
@

@@

<<ref.label = "scatter_by_local-2">>=
@

<<ref.label="make_scols-2">>=
@

<<ref.label="heat8-2">>=
@

<<ref.label = "make_scols-extra-2">>=
@

<<ref.label = "count_med">>=
@

<<ref.label = "heat9-2">>=
@

<<ref.label = "index-v-peak-position-2">>=
@

@@

<<ref.label = "more_setup-2">>=
@

<<ref.label="readRDS-2">>=
@

<<ref.label="make_local_annot-2">>=
@

<<ref.label = "make_nonlocal_annot-2">>=
@

<<ref.label = "make_local_annot2-2">>=
@

<<ref.label = "subset_expr_matrix-2">>=
@

<<ref.label = "tabulate-2", message=FALSE, warning = FALSE>>=
@

<<ref.label="make_pleio_tib-2">>=
@

<<ref.label = "make_pm-2">>=
@

@@

<<ref.label = "scatter_by_local-2">>=
@

<<ref.label="make_scols-2">>=
@

<<ref.label="heat8-2">>=
@

<<ref.label = "make_scols-extra-2">>=
@

<<ref.label = "count_med">>=
@

<<ref.label = "heat9-2">>=
@

<<ref.label = "index-v-peak-position-2">>=
@

<<>>=
hot_chr <- 2
@

@@

<<>>=
hot_chr <- 5
@

@@

<<>>=
hot_chr <- 7
@

@@

<<>>=
hot_chr <- 11
@

@@

<<>>=
hot_chr <- 13
@

>>>>

<<setuprnw, include=TRUE>>=
library(knitr)
opts_chunk$set(
concordance=TRUE,
echo = FALSE,
fig.lp = "fig:",
warning = FALSE,
message = FALSE,
comment = NA,
fig.dim = c(7, 7),
out.width = "\\linewidth"
)
def.chunk.hook  <- knitr::knit_hooks$get("chunk")
knitr::knit_hooks$set(chunk = function(x, options) {
  x <- def.chunk.hook(x, options)
  ifelse(options$size != "normalsize", paste0("\\", options$size,"\n\n", x, "\n\n \\normalsize"), x)
})
options(tinytex.verbose = TRUE)
@

@@

<<count_med>>=
n_med_tr <- 4 # arbitrary threshold
n_med_per_local <- med_tib %>%
  group_by(local_symbol) %>%
  filter(lod_diff > 1.5) %>%
  count() %>%
  filter(n >= n_med_tr)
n_med_per_local %>%
  arrange(desc(n)) %>%
  knitr::kable()

@@

<<heat9-2, fig.height = 7, fig.width = 7, out.width = "\\textwidth">>=
ord <- match(rn, rownames(pm))

p <- pm[ord, ord] %>%
  apply(FUN = trunc2, MARGIN = 2, threshold = 5) %>%
  heatmaply(Rowv = FALSE,
            Colv = FALSE,
            cexRow = 0.2,
            cexCol = 0.2,
            symm = TRUE,
            row_side_colors = scols[ord, ],
            col_side_colors = tibble(local = scols1[ord]),
            limits = c(0, 5)
            ) %>%
  hide_guides()
fnsvg <- paste0("Chr", hot_chr, "_heat", ".svg")
fnpdf <- paste0("Chr", hot_chr, "_heat", ".pdf")
plotly::orca(p, file.path("../figures", fnsvg))
plotly::orca(p, file.path("../figures", fnpdf))
p
@

@@

<<scatter_by_local-5, ref.label = "scatter_by_local-2">>=
@

@@

<<make_scols-extra-5, ref.label = "make_scols-extra-2">>=
@

<<count_med-5, ref.label = "count_med">>=
@

<<heat9-5, ref.label = "heat9-2">>=
@

<<index-v-peak-position-5, ref.label = "index-v-peak-position-2">>=
@

@@

<<more_setup-7, ref.label = "more_setup-2">>=
@

<<readRDS-7, ref.label="readRDS-2">>=
@

<<make_local_annot-7, ref.label="make_local_annot-2">>=
@

<<make_local_annot2-7, ref.label = "make_local_annot2-2">>=
@

<<subset_expr_matrix-7, ref.label = "subset_expr_matrix-2">>=
@

<<tabulate-7, ref.label = "tabulate-2", message=FALSE, warning = FALSE>>=
@

<<make_pleio_tib-7, ref.label="make_pleio_tib-2">>=
@

<<make_pm-7, ref.label = "make_pm-2">>=
@

@@

<<scatter_by_local-7, ref.label = "scatter_by_local-2">>=
@

<<make_scols-7, ref.label="make_scols-2">>=
@

<<heat8-7, ref.label="heat8-2">>=
@

<<make_scols-extra-7, ref.label = "make_scols-extra-2">>=
@

<<count_med-7, ref.label = "count_med">>=
@

<<heat9-7, ref.label = "heat9-2">>=
@

<<index-v-peak-position-7, ref.label = "index-v-peak-position-2">>=
@

@@

<<more_setup-11, ref.label = "more_setup-2">>=
@

<<readRDS-11, ref.label="readRDS-2">>=
@

<<make_local_annot-11, ref.label="make_local_annot-2">>=
@

<<make_local_annot2-11, ref.label = "make_local_annot2-2">>=
@

<<subset_expr_matrix-11, ref.label = "subset_expr_matrix-2">>=
@

<<tabulate-11, ref.label = "tabulate-2", message=FALSE, warning = FALSE>>=
@

<<make_pleio_tib-11, ref.label="make_pleio_tib-2">>=
@

<<make_pm-11, ref.label = "make_pm-2">>=
@

@@

<<scatter_by_local-11, ref.label = "scatter_by_local-2">>=
@

<<make_scols-11, ref.label="make_scols-2">>=
@

<<heat8-11, ref.label="heat8-2">>=
@

<<make_scols_extra-11, ref.label = "make_scols-extra-2">>=
@

<<count_med-11, ref.label = "count_med">>=
@

<<heat9-11, ref.label = "heat9-2">>=
@

<<index-v-peak-position-11, ref.label = "index-v-peak-position-2">>=
@

@@

<<more_setup-13, ref.label = "more_setup-2">>=
@

<<readRDS-13, ref.label="readRDS-2">>=
@

<<make_local_annot-13, ref.label="make_local_annot-2">>=
@

<<make_local_annot2-13, ref.label = "make_local_annot2-2">>=
@

<<subset_expr_matrix-13, ref.label = "subset_expr_matrix-2">>=
@

<<tabulate-13, ref.label = "tabulate-2", message=FALSE, warning = FALSE>>=
@

<<make_pleio_tib-13, ref.label="make_pleio_tib-2">>=
@

<<make_pm-13, ref.label = "make_pm-2">>=
@

@@

<<scatter_by_local-13, ref.label = "scatter_by_local-2">>=
@

<<make_scols-13, ref.label="make_scols-2">>=
@

<<heat8-13, ref.label="heat8-2">>=
@

<<make_scols-extra-13, ref.label = "make_scols-extra-2">>=
@

<<count_med-13, ref.label = "count_med">>=
@

<<heat9-13, ref.label = "heat9-2">>=
@

<<index-v-peak-position-13, ref.label = "index-v-peak-position-2">>=
@

<<def-2>>=
hot_chr <- 2
@

@@

<<def-5>>=
hot_chr <- 5
@

@@

<<def-7>>=
hot_chr <- 7
@

@@

<<def-11>>=
hot_chr <- 11
@

@@

<<def-13>>=
hot_chr <- 13
@
